Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-25 paper/paper.tex
Modify Data and Experiment sections.

@@

To obtain good $GoldSim$ values, we work with subsets consisting of item pairs
with at least either $N=40$ and $80$ common users. These choices are a
compromise between having enough data for statistically significant results and
having a sufficiently large $N$ that $GoldSim \approx TrueSim$. Note that even
with $N=80$ the average absolute error in $PearSim$ (i.e. $\left<\left| PearSim
- GoldSim \right|\right>$) is $\approx 0.1$\footnote{See Fig.
  \ref{fig:MSE_SimR}}.

...

First, we find pairs of items that have at least 
$N$ common users and calculate their $GoldSim$. Next, for each of these pairs
of items, we withhold user ratings, leaving $n$ common reviewers. This 
simulates a pair of items at a time when there is sparser rating data. 
We repeat this for $n=1,...,N$ to get varying degrees of sparsity. With the
sparse ratings alone, the model in question generates a prediction of the 
$GoldSim$, which is compared to the actual $GoldSim$. This is repeated over 
a large number of test pairs and the average squared error of the prediction 
is calculated for each $n$.

For this experiment, we use Amazon's book data. Books are rated by users on a 1
to 5 star-scale. Before any analysis of the data, we remove the biases from each
rating, as in \cite{Koren2009}:
\begin{align}
\hat{r_{ui}} = r_{ui} - \mu_r - b_i - b_u
\end{align}
where $r_{ui}$ is the raw rating user $u$ gave item $i$, $\mu_r$ is the average
rating over the entire dataset, $b_i$ is the item bias, calculated as the
average rating for item $i$ after $\mu_r$ has been subtracted from each, and 
$b_u$ is the user bias, calculated as the average rating from user $u$ after
$\mu_r$ and $b_i$ have been subtracted from each.

>>>>

Before any analysis of the data, we remove the biases from each rating, as in
\cite{Koren2009}:
\begin{align}
\hat{r_{ui}} = r_{ui} - \mu_r - b_u - b_i
\end{align}
where $r_{ui}$ is the raw rating user $u$ gave item $i$, $\mu_r$ is the average
rating over the entire dataset, $b_u$ is the user bias, calculated as the
average rating from user $u$ after $\mu_r$ has been subtracted from each, and
$b_i$ is the item bias, calculated as the average rating of item $i$ after
$\mu_r$ and $b_u$ have been subtracted from each.

@@

To obtain good $GoldSim$ values, we work with subsets consisting of item pairs
with at least either $N=40$ and $80$ common users. These choices are a
compromise between having enough data for statistically significant results and
having a sufficiently large $N$ that $GoldSim \approx TrueSim$. Note that even
with $N=80$ the average absolute error in $PearSim$ (i.e. $\left<\left| PearSim
- GoldSim \right|\right>$) is $\approx 0.1$ (see Fig.  \ref{fig:MSE_SimR}). So
  while $PearSim$ and $CosSim$ are relatively stable after this many common
users, there does remain a significant level of variance.

Our off-line experiment simulates the passing of time, applying ratings to items
in the order they actually occured. The similarity of item pairs is then
estimated each time a user has rated both items such that $N$ is incremented by
one. In this way, we can compare various estimators by comparing their outputs
to each other and to the known $GoldSim$ value for each pair. We proceed like
this for each pair in a test set for $n=1,...,N$ to get varying degrees of
sparsity. We then compute the average squared error of the estimate for each
$n$.
